Open Preprints in Ecology \& Evolution

### 2012-09-07 ms.tex
Fleshed out paragraphs

arXiv (\href{http://arxiv.org/}{http://arxiv.org/}) is the most
widely-used preprint server available today, and its use is almost
universal in mathematics and most branches of physics.  arXiv receives
over 7,000 submissions per month
(http://arxiv.org/show_monthly_submissions).  Paul Ginsparg originated
ArXiv for high-energy physicists to communicate preprints via email
and ftp.  Soon after its origination the world-wide web became
available.

Submission to arXiv is fully automated via the world-wide web.
Authors can submit LaTeX documents or directly in PDF format.  A
moderation system was put in place in 2004: papers must be categorized
by a moderator.  At least one author of a paper must be an
``endorser'' that has previously submitted a paper or has received
permission to submit.  Endorser status is automatic for members of
recognized academic institutions.

Most papers posted to arXiv are eventually printed in journals.  There
are notable exceptions, including Perelman's landmark paper solving
the Poincar\'{e} conjecture \cite{2002math.....11159P}.

arXiv is now administered by the Cornell University Libraries.
Funding comes from voluntary pledges by academic institutions along
with matching funds from the Simons Foundation \cite{arxiv_future}.
One-hundred twenty six of the top two-hundred institutions in terms of
downloads have provided the operating budget for arXiv over the next
five years.  This plan reduces the financial burden on Cornell
University and transfers governance to a collaborative community in
accordance with arXiv's key principles.

>>>>

arXiv (\url{http://arxiv.org/}) is the most widely-used preprint
server today, and its use is almost universal in mathematics and most
branches of physics.  Physicist Paul Ginsparg originated arXiv in 1991
for theoretical high-energy physicists to communicate preprints via
email and ftp, and soon thereafter adopted the newly created
world-wide web\cite{jackson2002preprints}.  arXiv now receives over
7,000 submissions per month
(\url{http://arxiv.org/show_monthly_submissions}).  arXiv divides its
submissions into subcategories of physics, mathematics, computer
science, quantitative biology, finance and statistics.  The
quantitative biology category includes subcategories for Populations
and Evolution, Quantitative Methods and other categories that may be
of interest to ecologists and evolutionary biologists.
% Check me on this @Pierre!  Not only is this vague, but I'm not sure
% how to verify it; I want to give people the impression that a
% "Quantitative ecology" or "General ecology" category could be
% created easily
The creation of new categories is regulated by the same system that
categorizes papers.

Submission to arXiv is fully automated via the world-wide web.
Authors can submit \TeX{}/\LaTeX{} documents or directly in PDF or
PostScript (for example, as exported by a word processor).  A
moderation system was put in place in 2004: papers must be categorized
by an ``endorser.''  At least one author of a paper must be an
endorser that has previously submitted a paper or has received
permission to submit to a particular category.  Many authors in
mathematics and physics submit papers as soon as they are ready for
review by colleagues, although another popular option is submitting
simultaneously to a journal and arXiv.

Most papers posted to arXiv are eventually printed in journals.  There
are notable exceptions, including Perelman's landmark paper leading to
the proof of the Poincar\'{e} conjecture \cite{2002math.....11159P}.
arXiv provides a reliable citation system for all eprints (see our
citation \cite{2002math.....11159P}), lending a form of ``intellectual
priority'' to works posted there.  Despite these marks of arXiv 
functioning as a scientific journal, arXiv has never sought to replace
scientific journals and explicitly states that it serves a different
function as ``an openly accessible, moderated repository for scholarly
articles in specific scientific disciplines.''

arXiv is now administered by the Cornell University Libraries.
Funding comes from voluntary pledges by academic institutions along
with matching funds from the Simons Foundation \cite{arxiv_future}.
One-hundred twenty six of the top two-hundred institutions in terms of
downloads have provided the operating budget for arXiv over the next
five years.  This plan reduces the financial burden on Cornell
University and transfers governance to a collaborative community in
accordance with arXiv's key principles.  arXiv takes numerous measures
to ensure that the repository will remain permanently available and
submissions will be readable.
